Analysis for Non-Expressive performances (ONSET)

### 2020-04-09 material/analysis/stim_n/ioi_onset.Rmd
modify layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
## Individual
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

@@

## Exclude outlier participants
```{r cv_outlier, echo = FALSE}
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]

>>>>

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

@@

### Exclude outlier participants
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)
